---
title       : What makes a job prestigious? 
subtitle    : Education? Income? Gender parity?
author      : Katiter
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## The Census Data


With this simple Shiny application, we let the user explore the Canadian census data for occupations, available in the `car` package.

```{r}
Prestige <- car::Prestige
head(Prestige)
```
 

---
## Variables of Interest


The user can explore how these factors correlate wht the perceived respectability of an occupation:

- Gender
- Education
- Salary

---

## A Sample Plot

For example, how does occupational prestige correlate with years of education? 

```{r, echo=FALSE}
require(ggplot2)
ggplot(Prestige, aes(education, prestige)) + geom_point() + theme_bw()
```

## Another Sample Plot
In the Shiny app, you can also explore by the percentage of women or by job type.


```{r, echo=FALSE}
require(ggplot2)
ggplot(Prestige, aes(education, prestige)) + geom_point(aes(size=women, color=type)) + theme_bw()
```


---

## A Simple Model

After the exploratory analysis, we can also build a simple model to describe occupational prestige.

```{r, echo=FALSE}
model <- lm(prestige ~ education + income, data=Prestige)
summary(model)
```




